% latex article template

% cheat sheet(eng): http://www.pvv.ntnu.no/~walle/latex/dokumentasjon/latexsheet.pdf
% cheat sheet2(eng): http://www.pvv.ntnu.no/~walle/latex/dokumentasjon/LaTeX-cheat-sheet.pdf
% reference manual(eng): http://ctan.uib.no/info/latex2e-help-texinfo/latex2e.html

% The document class defines the type of document. Presentation, article, letter, etc. 
\documentclass[12pt, a4paper]{article}

% packages to be used. needed to use images and such things. 
\usepackage[pdfborder=0 0 0]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\PassOptionsToPackage{hyphens}{url}

% hides the section numbering. 
\setcounter{secnumdepth}{-1}

% Graphics/image lications and extensions. 
\DeclareGraphicsExtensions{.pdf, .png, .jpg, .jpeg}
\graphicspath{{./images/}}

\title{
	Architectural Design Document \\
    TDT4240 - Group A14 \\
	\\
	\normalsize{
	\underline{Framework:} \\ 
	Android\\
    \\
	\underline{Quality Attributes:} \\
	Primary: Modifiability \\
	Secondary: Useability \\ 
    \\
	}
}
\author{
	\underline{Group members:} \\
    Bremnes, Jan A. S.\\
    Johanessen, Stig Tore\\
	Hesselberg, Håkon \\
    Kirø, Magnus L.\\
	Randby, Simon \\
    Tørresen, Håvard\\
}
\date{\today}

\begin{document}
\maketitle
\pagenumbering{arabic}

\newpage
\tableofcontents
\newpage

primary + secondary quality attribute. 

\section{introduction}
Project description
document structure and phase (requirement)

game description

\section{Architectural drivers / architectural significant requirements (asr)}
the main drivers(functional, quality and business requirements) that affect the architecture the most 

\section{Stakeholders and concerns}
the stakeholders and their concerns. 

\section{Selection of Architectural views (viewpoint)}
* a list of views that you will use in the architectural design, their purpose, target audience(which stakeholders are you addressing), and what notation will be used for each view. 

* all groups need  to choose at least a logical view, a process view and a development view or similar. 

\section{architectual tactics}
describe the tactics for architecture to meet the quality requirements. 

\section{Architectural and design pattern}
selection of arcitectural/design patterns to be used in your architectue..

\section{views}
document architecture using your selected views (at least logical, process and development) through diagrams and supporting/explaining text.

\section{consistency among views}
descripion inconsistencies among the vieas in your architecture.

\section{architectural rationale}
hehe you will explain why you have chosen the architecture will work and fulfill the quality, business and the functional requirements.

\section{issues}
describe issues you faced working with and describing the architecture.

\section{references}
A list of any references books, articles, web-pages, documents etc, that you have used. 

\section{changes}
to be describes changes carried out with this document from first draft until final delivery including all improvements based on feedack from course staff and others. 

\end{document}
