% latex article template

% cheat sheet(eng): http://www.pvv.ntnu.no/~walle/latex/dokumentasjon/latexsheet.pdf
% cheat sheet2(eng): http://www.pvv.ntnu.no/~walle/latex/dokumentasjon/LaTeX-cheat-sheet.pdf
% reference manual(eng): http://ctan.uib.no/info/latex2e-help-texinfo/latex2e.html

% The document class defines the type of document. Presentation, article, letter, etc. 
\documentclass[12pt, a4paper]{article}

% packages to be used. needed to use images and such things. 
\usepackage[pdfborder=0 0 0]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\PassOptionsToPackage{hyphens}{url}

% hides the section numbering. 
\setcounter{secnumdepth}{-1}

% Graphics/image lications and extensions. 
\DeclareGraphicsExtensions{.pdf, .png, .jpg, .jpeg}
\graphicspath{{./images/}}

\title{
	Project Implementation \\
    TDT4240 - Group A14 \\
	\\
}
\author{
	\underline{Group members:} \\
    Bremnes, Jan A. S.\\
    Johanessen, Stig Tore\\
	Hesselberg, Håkon \\
    Kirø, Magnus L.\\
	Randby, Simon \\
    Tørresen, Håvard\\
}

\date{\today}

\begin{document}
\maketitle
\paragraph{Chosen COTS:} Andoid
\paragraph{Primary quality attribute:} Modifiability
\paragraph{Secondary quality attribute:} Testability \\

\pagenumbering{arabic}

\begin{abstract}
This is the paper's abstract \ldots
\end{abstract}

\newpage
\tableofcontents
\newpage

\section{Introduction}
What, why, where.
\subsection{Test phase description}
\subsection{Implementation phase description}
\subsection{Game consept description}
\subsection{Document Structure}

\section{Design/Implementation details}
\subsection{Program design}
\subsection{Diagrams}
\subsection{Class descriptions}

\section{User Manual}
\subsection{Installation}
Description of how to install, compile and run the game/robot.
\subsection{Gameplay}
description of how to play the game. 
\subsection{Screenshots}
Screenshots from the game

\section{Test report}
\subsection{Funtional requirements}
The report should contain test reports for both functional requirements and 
\subsection{Quality requirements}
quality requirements (quality scenarios).
\subsection{Test reports}
-Test reports must include requirement ID (e.g. F1, F2, A2, A3..), 
-description of requirement, who did the test, date for test, time used, 
-evaluation (failure/success) and comment (discussion/comment about the result). 
\subsection{Quality requirements}
Quality requirement tests must in addition include stimuli, expected 
response measure, and observed response measure. 

\section{Architecture Relationship}
\subsection{Implementation deviations}
-This section should list the inconsistencies between your architecture and 
the implementation. Give the reasons for these inconsistencies. 
-Discuss whether they could have been discovered at an earlier point, for
instance during the ATAM evaluation.

\section{Issues}
\section{Future work}
\section{Discussion}


\end{document}
